Project 2

### 2015-04-24 project2/paper/main.tex
Adding conclusion section

% Talking points
% - Average between station time
% - Rosslyn to Stadium Armory time is consistent
% - Robustness to changes in track availability

Unsurprisingly, WMATA plans its trains effectively to be robust to a fair amount track outages, while still providing
the timings estimated on their website.

>>>>

Empirically measuring between station times is a very granular way to measure the accuracy of WMATA's predictions. For
instance, stations within DC are estimated between 1 and 2 minutes, resulting in a travel time from Rosslyn to
Stadium-Armory taking 21 minutes. Based on the between station data we collected, we estimate empirically this actaully
ends up being around 24 minutes and 8 seconds. This discrepancy can be explained by a few reasons, the first being that
WMATA is wrong. This is of course, a potential case, but I'm more sure that this really an indication of issues in the
dataset itself. Since rail predictions are only precise to the minute, stations that are only a minute apart have the
potential to cause aliasing when calculating between station times. This may be the reason some of the interior station
times are 2 minutes instead of 1. Moreover, because this was a global measurement over a period of time, I may have 
captured some delaying event that caused between station times to diminish to a great enough value for a long enough
time to ``pull'' the mean up.

Regardless of these discrepancies, the simulation appears to agree with the estimates. Trains moving westward average
around 22.15 minutes to reach Rosslyn from Stadium-Armory. Eastward trains perform slightly better, hovering closer to
21 minutes. Both distributions, without any track disturbances, are very tight with little variance. The difference in
means is accounted for by the empirical measurement of between station times. The total westward time from Rosslyn to
Stadium-Armory is roughly 30 seconds shorter than the eastward counterpart. The remaining time may be accounted for by
the Rosslyn-Foggy Bottom connection, the most western connection in the system. The between station time here is 
consistently 3 minutes, rather than 2. Because of this, arriving trains may be forced to wait more often. However,
because our scope is narrowed for this project, we may be missing some other behavior further westward that may explain
this behavior.

Unsurprisingly, WMATA plans its trains effectively to be robust to a fair amount track outages, while still providing
the timings estimated on their website. Even with three tracks disabled, the mean travel time of eastern and western
trains still hovers around 23 minutes and 30 seconds. However, worth noting is that the \emph{variabilty} increases
drastically. Even though the mean moves little, there still are some trains that end up taking over 40 minutes to
reach the other side given these conditions. In a way, this is simply ``bad luck'' on that particular train's part,
simply because it's timing fell so that it arrived right as another train had occupied the track (with potentially
other trains waiting already). However as more tracks become disabled, the bad luck slowly becomes more likely for any
train to experience.
